On Better Bound on VOI of Monte Carlo Sampling

### 2011-09-21 paper/voisam/onbetterbound.tex
spell checked

The minimum of $V^*$ is achieved when $\frac {dV^*} {d\gamma}=0$, that
is, when $\gamma$ is the root of the following equation:
\[ 4\beta n(\alpha-\gamma)=\exp\left(-2n\left(\frac {\alpha-\beta}
    {\alpha-\gamma}\right)^2\right) \]
If a root in the interval  $0\le\gamma\le\beta$ exists, then the
number of samples is bounded as
\[n\le\frac 1 {4\beta(\alpha-\beta)}\]
by observing that the righthand side 
is at most $1$ (a negative power), and the left-hand side is at least
$4\beta n(\alpha-\beta)$.
So, the bound can supposedly be improved for smaller values of
$n$. The improvement is more significant when the current best and
second-best sample means are close.

@@

A closed-form solution for $\gamma$ cannot be achieved, but the value
can be efficiently computed. It should be determined empirically
whether the improved estimate has justified influence on the
performance of the algorithm.

>>>>

The minimum of $V^*$ is achieved when $\frac {dV^*} {d\gamma}=0$, that
is, when $\gamma$ is the root of the following equation:
\[ 4\beta n(\alpha-\gamma)=\exp\left(-2n\left(\frac {\alpha-\beta}
    {\alpha-\gamma}\right)^2\right) \]
If a root in the interval  $0\le\gamma\le\beta$ exists, then the
number of samples is bounded as
\[n\le\frac 1 {4\beta(\alpha-\beta)}\]
by observing that the right-hand side 
is at most $1$ (a negative power), and the left-hand side is at least
$4\beta n(\alpha-\beta)$.
So, the bound can supposedly be improved for smaller values of
$n$. The improvement is more significant when the current best and
second-best sample means are close.

@@

A closed-form solution for $\gamma$ cannot be obtained, but given
$\alpha, \beta, n$, the value of $\gamma$ can be efficiently
computed. It should be determined empirically whether the improved
estimate has justified influence on the performance of the algorithm.
